\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-06-15 doc/incertae_sedis.tex
Update Discussion.

%\newcommand{\mthcomment}[1]{{\color{red} #1}\xspace}
\newcommand{\mthcomment}[1]{}

%\newcommand{\bdrcomment}[1]{{\color{cyan} #1}\xspace}
\newcommand{\bdrcomment}[1]{}

@@

\section{Discussion}

In this paper we've described a method for handling \emph{incertae sedis} taxa
when constructing taxonomic supertrees.  Our method incorporates the uncertain
placement information from such taxa when constructing the supertree.  It also
handles higher taxon names and allows input trees to revise the taxonomy by
determining where \emph{incertae sedis} taxa should be placed.

However, our method leaves a number of problems for future work.  One of these
problems is that we consider taxa with an \emph{incertae sedis} label to 
about which siblings in attach within.  However, in practice,
the taxonomist may only consider it plausible for the taxon to intrude only within specific
siblings.  Our method also assumes that an \emph{incertae sedis} label on a taxon
indicates that a taxon may attach at any depth within its siblings.  In practice, an
\emph{incertae sedis} genus with sister families (for example) is unlikely to attach
so deeply within a sister family that it becomes nested within another genus.

>>>>

\newcommand{\mthcomment}[1]{{\color{red} #1}\xspace}
%\newcommand{\mthcomment}[1]{}

\newcommand{\bdrcomment}[1]{{\color{cyan} #1}\xspace}
%\newcommand{\bdrcomment}[1]{}

@@

\section{Discussion}
\bdrcomment{This is slightly exaggerated in the sense that there might be other
  frameworks to incertae sedis taxa that do not require these exact moves.  Nonetheless,
  I think this is not just a ``review'', in the sense that any well-founded approach
  would have to work through all of these problems.  By working through them, we have
  navigated the paths that subsequent approaches will need to walk.

  I would argue that
  the fact that our solution seems relatively simple should be seen as a success, and not
  a sign that we haven't done enough work.  It often takes a lot of work to get a complex
  solution down to a simple solution.

  Additionally, the fact that we do not have
  a lot of ``results'', in the sense of (say) large number of higher-taxon names that
  are rescued by avoiding the naive approach, is a result of the fact that we didn't want
  to do the work to add more input phylogenies with incertae sedis tips that will cause
  problems.  We could always go back and try to get these ``results'', but the percieved value
  wasn't very high.  Also, the algorithm that we came up with is itself a ``result''.
}

This paper introduces the necessary concepts and methods for handling \emph{incertae sedis}
taxa in taxonomic supertrees.  We describe the goals of preserving internal edges,
preserving higher taxon names, and preserving the opportunity to revise the taxonomy
based on placement of \emph{incertae sedis} taxa.  In addition to explaining why
the naive approach to taxonomic supertrees that ignores incertae sedis taxa sacrifices
these three goals, we introduce a simple and satisfying way to achieve these goals
through defining rooted splits for taxonomy edges with reduced exclude sets.  We also
provide a simple and efficient recursion for computing these splits.

Despite the simplicity of our approach, some complexities and conceptual difficulties
remain.  While the correspondence of nodes and names is a simple one-to-one and onto
relationship without \emph{incertae sedis} taxa, when \emph{incertae sedis} taxa are
introduced, the relationship might be neither one-to-one (Figures \ref{fig:Multiple-names-can},\ref{fig:interdigitation}) nor onto (Figure \ref{fig:One-name-can}).
This necessitates putting more thought into the semantics of taxon names, including
whether names might become synonyms.  This may be considered a ``complexity''.

In addition, our attempt to define reduced exclude sets for taxonomy splits yields
a semantics that is not the only concievable semantics for \emph{incertae sedis}
taxa (Figure \ref{fig:Placing-one-incertae}).  It allows \emph{incertae sedis} siblings to inter-digitate
(Figure \ref{fig:interdigitation}), which might be a surprising result to the taxonomist.  Furthermore,
in what might seem a lack of consistency, it does \emph{not} allow \emph{incertae sedis}
taxa to intrude into each other if they become siblings through the result of
placement, as is the case for taxa W and V in Figure \ref{fig:Placing-one-incertae}c.
While each of these problems can be solved separately by adjusting the definition of the
reduces exclude sets, no solution seems to be best in all respects.  This may be a result
of the fact that split-based approaches to supertrees seek a simultaneous solution to a set
of constraints.  This simultaneity can be contrasted with a solution that is phrased
as a set of sequential operations to the taxonomy, as would be the case when (for example)
(i) placing V within WX so that it is sister to W, (ii) marking V as no longer incertae sedis, and then (iii)
placing W within V (which is no longer incertae sedis).  This maybe considered a ``conceptual difficulty''.

Another issue that we have postponed for future work is how to more narrowly delimit
the ranges in which \emph{incertae sedis} may attach.  The current paper allows
\emph{incertae sedis} to attach anywhere within their sisters, but the taxonomist
may only consider it plausible for the taxon to intrude only within specific
siblings.  Furthermore, our method also assumes that an \emph{incertae sedis} label on a taxon
indicates that a taxon may attach at any depth within its siblings.  In practice, an
\emph{incertae sedis} genus with sister families (for example) is unlikely to attach
so deeply within a sister family that it becomes nested within another genus.
